\cvsection{Experience}
\begin{cventries}
  \cvexperience
    {Director, Data \& Analytics}
    {xG Health Solutions (powered by Geisinger)}
    {Columbia, MD}
    {9/2016 - Present}
    {Value-based care consulting firm spun out of Geisinger Health System, which maintains majority ownership. Serve as Engagement Lead for xG’s analytic strategy engagements and bridge between xG’s Analytics unit and clinical strategy team. Specializes in helping large health system clients leverage their data assets to improve performance under risk-based contracts. Promoted from Senior Advisor to Director in March, 2018.}
    {
      \begin{cvitems}
              \item {Engagement Lead helping large integrated health system optimize patient outcomes in preparation for launching a Medicare Advantage plan. Led team that analyzed claims data for 45K lives currently at risk (~\$400M total medical + rx spend) and presented report to client's C-level leadership identifying \$58M of cost of care savings or increased revenue, broken out into "shovel-ready" clinical initiatives that are prioritized by opportunity size. Currently working with client's clinical leadership team to implement report's action plan as part of high-level xG team that includes  ex-CMO's of Geisinger and Ochsner Health Systems. Led team of four.}
                 \item {Oversaw Analytics-as-a-Service engagement involving data acquisition, mapping, analysis, and delivery via Cerner's HealtheIntent platform. Guiding client through an Agile development process, helping facilitate governance committees that will triage and prioritize new analytic report requests. Led team of eight.}
              \item {Designed and implemented a comprehensive, \$160M Pay-for-Performance (DSRIP) program in a large academic health system covering over 230K Medicaid lives. Led development of patient attribution algorithms for various provider types (PCPs, behavioral health, SNFs, hospitals). Created rules for provider performance measurement, patient targeting, settlement/appeals governance, and funds distribution. Worked with client's executive team and Cerner to QA and implement program in Cerner's HealtheIntent platform. }
               \item {Developed clinical analytics framework to power a High Performance Network and commercial bundled payment model for a national alliance of over 42 self-insured employers with 7M covered lives. Worked with clinical expert panel to source best practice recommendations and KPIs. Collaborating with major national payers to execute network rollout.}
               \item {Tapped by xG senior executives to join product managment/sales strategy leadership teams for our Client Analytics unit and the company as a whole.}
             \end{cvitems}
    }

  \cvexperience
    {Chief Medical Officer}
    {Artemis Health}
    {Salt Lake City, UT}
    {6/2015 - 9/2016}
    {Population health SaaS company that provides an analytics and data warehousing platform that helps self-insured employers identify waste and low-quality care, suggests solutions to reduce both, and tracks the efficacy of these solutions. Reporting directly to CEO, served as acting CMO to help company reach successful institutional fundraising round.}
    {
      \begin{cvitems}
              \item {Served on company's 5-person leadership team, acted as bridge between  sales, clinical, and engineering teams. Prioritized company strategy and roadmap based on clinical impact and feedback from clients. }
               \item {Led product development for several key features of Artemis's primary software application, including  episodes-of-care, automated data quality assessment, and machine learning models that predict member actions.}
               \item {Generated over \$300K annualized recurring revenue while pitching clients with sales team.}
               \item {Participated in presentations to venture capital firms.}
             \end{cvitems}
    }
  \cvexperience
    {Program Manager, Learning Health Systems}
    {The Children's Hospital of Philadelphia}
    {Philadelphia, PA}
    {6/2014 - 1/2016}
    {Directly managed \$500K of research budget related to CHOP's Learning Health System project portfolio, including NIH's Global Rare Diseases Repository (GRDR) and PEDSNet, an 8-hospital research and quality improvement collaboration with shared EHR data for 5M children and 100M encounters. PEDSnet is backed by over \$15M of federal funding and is led by former team at CHOP.}
    {
      \begin{cvitems}
              \item {Managed five team members across three projects.}
               \item {Directed two large technical projects: (1) PEDSnet's web platform (http://www.pedsnet.org). \$100K, three developers; (2) software to enable rare disease organizations to standardize their data without technical help. \$50K, two developers.}
               \item {Negotiated industry partnerships with Express Scripts (NASDAQ: ESRX) and QuintilesIMS (NYSE: Q).}
               \item {Oversaw design and implementation of a data integration pipeline for rare disease data, developing novel natural language processing algorithms to assist with translation of clinical data to industry-standard vocabularies (SNOMED-CT and RxNorm). \$350K budget, five informatics researchers.}
             \end{cvitems}
    }
  \cvexperience
    {Board Member, Founding CEO}
    {Global Development Collaborative}
    {Philadelphia, PA}
    {5/2010- Present}
    {GDC is a 501(c)(3) non-profit organization that improves the standard of living in developing countries by providing interest-free loans and business development assistance with product design, branding, packaging, and distribution to help community members start a business selling handmade crafts.}
    {
      \begin{cvitems}
              \item {As founding CEO, designed programs that continue to be GDC's core offerings.}
               \item {Starting with zero funding, GDC's programs have generated more than \$200K. All proceeds from our programs are re-invested into the community's business endeavors and infrastructure.}
             \end{cvitems}
    }

\end{cventries}
